---
title: "Filtering and extracting information from a regulon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Filtering and extracting information from a regulon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(tibble)
library(readr)
```

## Overview

This vignette demonstrates how to post-process a regulon object generated with `corto()`, using two helper functions:

- `filter_regulon()`: to filter interactions based on transcription factors, likelihood, and correlation.
- `getregulon()`: to convert the filtered regulon into a tidy data frame.

We will use a small precomputed example regulon saved as an `.rds` file in the package.

---

## Load example regulon

```{r load}
regulon_path <- system.file("extdata", "example_regulon.rds", package = "corto")
regulon <- readRDS(regulon_path)
```

---

## Filter regulon by likelihood and correlation

```{r filter}
filtered <- filter_regulon(
  regulon = regulon,
  tf_list = names(regulon),
  likelihood_threshold = 0.75,
  correlation_threshold = 0.2
)
```

---

## Convert to tibble

```{r tibble}
regulon_df <- getregulon(
  regulon = filtered,
  likelihood_threshold = 0.75
)

head(regulon_df)
```

---

## Export to file (optional)

You can also export the result to a TSV file:

```{r export, eval = FALSE}
getregulon(
  regulon = filtered,
  likelihood_threshold = 0.75,
  export = TRUE,
  filename = "filtered_regulon.tsv"
)
```

---

## Summary

With these tools, it becomes easier to analyze and visualize a regulon created with `corto`, especially when focusing on a subset of transcription factors or robust interactions.

